Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
tidy

netTS
-->

@@

Our case study integrates variation in temporal and spatial scale
to assess the role of scale in predicting multilayer networks. As one might
expect, we found increasing social threshold results in saturation of potential
social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
to generate social networks during times when animals are engaged in different
behaviours, including travelling, interacting, or foraging [@Muller_2018;
@Finn_2019] and construct a multilayer network based on behaviour-specific
monolayer networks [e.g. @Smith_Aguilar_2019].

## Habitat selection and space use

# Conclusions

<!-- TODO: push gps data, HMM networks, etc-->

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

@@

<!-- TODO: In summary, -->

>>>>

Another potential application would be
to generate social networks during times when animals are engaged in different
behaviours, including travelling, interacting, or foraging [@Muller_2018;
@Finn_2019] and construct a multilayer network based on behaviour-specific
monolayer networks [e.g. @Smith_Aguilar_2019].

netTS

However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015].

With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017].

-->

@@

# Conclusions
Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

@@
